---
title: "Group Project - Group #41"
author: "STAT 420, Summer 2018, Gassan Soukaev, Hanna Loboda, Hao Tang, You Li"
date: ''
output:
  html_document: 
    toc: yes
  pdf_document: default
urlcolor: cyan
---

***

```{r setup}
options(scipen = 1, digits = 4, width = 80, fig.align = "center")
```

## Introduction

### Team
* Gassan Soukaev (soukaev2)
* Hanna Loboda (hloboda2)
* Hao Tang (haot3)
* You Li (youl3)

### Project Description
Titanic - Who was likely to survive?

“The sinking of the RMS Titanic is one of the most infamous shipwrecks in history.  On April 15, 1912, during her maiden voyage, the Titanic sank after colliding with an iceberg, killing 1502 out of 2224 passengers and crew. This sensational tragedy shocked the international community and led to better safety regulations for ships.

One of the reasons that the shipwreck led to such loss of life was that there were not enough lifeboats for the passengers and crew. Although there was some element of luck involved in surviving the sinking, some groups of people were more likely to survive than others, such as women, children, and the upper-class.”

The purpose of this analysis will be to ascertain any patterns in the survival of the passengers by identifying any attributes that would make you more likely to survive amidst all the chaos.

### Data
```{r}
ptitanic = read.csv("train.csv")
str(ptitanic)
```
This dataset is available at kaggle: https://www.kaggle.com/c/titanic/data

Response:

* survival is the response variable (0 = No, 1 = Yes)

Predictors:

* Pclass - Ticket class (1 = 1st, 2 = 2nd, 3 = rd)
* Sex (Male, Female)
* Age - Age in years (Numeric)
* SibSp - Number of siblings / spouses aboard the Titanic
* parch - Number of parents / children aboard the Titanic
* ticket - Ticket number
* fare - Passenger fare
* cabin - Cabin number
* embarked - Port of Embarkation (C = Cherbourg, Q = Queenstown, S = Southampton)

## Methods
- First of all let's do some data cleanup
- We don't need columns such as PassengerID, Name, Ticket # as they have no impact on our statistical analysis
- Let's remove them leaving only numeric and factor columns

```{r}
ptitanic = subset(ptitanic, select = c(2, 3, 5, 6, 7, 8, 10, 12))
str(ptitanic)
head(ptitanic)
```

- Now let's see if we have missing values

```{r}
apply(is.na(ptitanic),2,sum)
```

- Yes, out of 891 rows we have 177 records with missing Age which is quite substantial chunk of data
- Removing all of them may not be as good of an idea since it represents 20% of the total training data
- We will replace NA values with the average age (which happens to be 30)

```{r}
library(zoo)
ptitanic$Age = round(na.aggregate(ptitanic$Age))
```

- Let's check for missing values now

```{r}
apply(is.na(ptitanic),2,sum)
```

- All good! Ready to do the analysis. Let's get to know our data. Let's take a look at pairs plot and look for any patterns or collinearity among the predictors

```{r}
pairs(ptitanic, col = "dodgerblue")
```

- No clear patterns or collinearity issues can be seen

- Let's take a quick look at collinearity matrix for numeric variables

```{r}
round(cor(ptitanic[c(1:2, 4:7)]), 2)
```

- The collinearity matrix shows some collinearity between number of parents / children aboard and # of siblings / spouses aboard which makes sense
- There is also some collinearity between Fare and Ticket class which also makes sense

- Time to start looking at the linear regression models
- Let's start with building a simple additive model

```{r}
add_model = glm(Survived ~ ., data = ptitanic, family = binomial)
summary(add_model)
```




## Results


## Discussion


## Appendix
