---
title: "Group Project - Group #41"
author: "STAT 420, Summer 2018, Gassan Soukaev, Hanna Loboda, Hao Tang, You Li"
date: ''
output:
  html_document: 
    toc: yes
  pdf_document: default
urlcolor: cyan
---

***

```{r setup}
options(scipen = 1, digits = 4, width = 80, fig.align = "center")
```

## Introduction

### Team
* Gassan Soukaev (soukaev2)
* Hanna Loboda (hloboda2)
* Hao Tang (haot3)
* You Li (youl3)

### Project Description
Titanic - Who was likely to survive?

“The sinking of the RMS Titanic is one of the most infamous shipwrecks in history.  On April 15, 1912, during her maiden voyage, the Titanic sank after colliding with an iceberg, killing 1502 out of 2224 passengers and crew. This sensational tragedy shocked the international community and led to better safety regulations for ships.

One of the reasons that the shipwreck led to such loss of life was that there were not enough lifeboats for the passengers and crew. Although there was some element of luck involved in surviving the sinking, some groups of people were more likely to survive than others, such as women, children, and the upper-class.”

The purpose of this analysis will be to ascertain any patterns in the survival of the passengers by identifying any attributes that would make you more likely to survive amidst all the chaos.

### Data
```{r}
ptitanic = read.csv("test.csv")
str(ptitanic)
```
This dataset is available at kaggle: https://www.kaggle.com/c/titanic/data

Response:

* survival is the response variable (0 = No, 1 = Yes)

Predictors:

* Pclass - Ticket class (1 = 1st, 2 = 2nd, 3 = rd)
* Sex (Male, Female)
* Age - Age in years (Numeric)
* SibSp - Number of siblings / spouses aboard the Titanic
* parch - Number of parents / children aboard the Titanic
* ticket - Ticket number
* fare - Passenger fare
* cabin - Cabin number
* embarked - Port of Embarkation (C = Cherbourg, Q = Queenstown, S = Southampton)

## Methods
The methods section should contain the bulk of your “work.” This section will contain the bulk of the R code that is used to generate the results. Your R code is not expected to be perfect idiomatic R, but it is expected to be understood by a reader without too much effort. Use RMarkdown and code comments to your advantage to explain your code if needed.

This section should contain any information about data preparation that is performed to the original data before modelling. Then you will apply methods seen in class, which may include some of the following but are not limited to:

* Multiple linear regression
* Dummy variables
* Interaction
* Residual diagnostics
* Outlier diagnostics
* Transformations
* Polynomial regression
* Model selection

Your task is not to use as many methods as possible. Your task is to use appropriate methods to find a good model that can correctly answer a question about the dataset, and then to communicate your result effectively.

## Results
The results section should contain numerical or graphical summaries of your results. You should report a final model you have chosen. There is not necessarily one, singular correct model, but certainly some methods and models are better than others in certain situations. You may use any methods we studied this semester to complete this task, and provide evidence that your final choice of model is a good one.

## Discussion
The discussion section should contain discussion of your results and should frame your results in the context of the data. How is your final model useful?

## Appendix
The appendix section should contain code and analysis that is used, but that may clutter the report or is not directly related to the choice of model.